Testing the motor and cognitive foundations of Paleolithic social transmission

### 2021-08-18 manuscript/manuscript.Rmd
replace the figure 14.

```{r fig7, echo=FALSE, out.width = '100%', fig.align='center', fig.cap="Results showing significant differences between the instructor (expert) and novice flaking performance."}
knitr::include_graphics(here::here("figure/Figure7.png"))
```

@@

```{r fig13, echo=FALSE, out.width = '100%', fig.align='center', fig.cap="Two significant interaction effects of training condition, social information, and visuo-spatial working memory on overall flaking productivity."}
knitr::include_graphics(here::here("figure/Figure13.png"))
```

>>>>

```{r fig7, echo=FALSE, out.width = '100%', fig.align='center', fig.cap="Results showing significant differences between the instructor (expert) and novice flaking performance."}
knitr::include_graphics(here::here("figure/Figure7.jpg"))
```

@@

```{r fig13, echo=FALSE, out.width = '100%', fig.align='center', fig.cap="Two significant interaction effects of training condition, social information, and visuo-spatial working memory on overall flaking productivity."}
knitr::include_graphics(here::here("figure/Figure13.jpg"))
```
